Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-04-26 Ben_Manuscripts/structure_paper/Outline.tex

  %BJC3: Feel free to suggest different words
  \subsection{Density of monomers around pores}
  Our simulations best support a model built with 5 monomers per layer based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 monomers per layer. 
  \begin{itemize}  
  		\item We built systems in both the parallel displaced and sandwiched configurations 			with layers initially spaced 3.7 \AA~apart according to the dry equilibration 
  		procedure.
  		\item The pore-to-pore spacing is stable in all systems are stable after 400 ns of 
  		simulation. Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all 
  		systems tested. 
  		\item Systems built with 5 monomers in each layer equilibrate to a pore spacing that is 
  		most consistent with the experimental value of 4.12 nm derived from SAXS measurements 
	    (Figure~\ref{fig:SAXS}).
  \end{itemize}

@@

  The simulated XRD patterns produced from both systems show moderate qualitative 
  agreement with experiment. 
  \begin{itemize}
  		\item R-alkanes and R-pores appear in the expected location
		\item R-pores is more intense than experiment, likely because we are simulating a 
		perfect, infinite hexagonal array. The real system has defects and domain misalignment
	    which decreases the overall intensity.
	    \item R-$\pi$ appears at a lower $q_z$ value than experiment. In both systems, the
	    reflection reaches its maximum at c.a. $q_z=1.4$ which means that monomers prefer 
	    to stack c.a. 4.5 \AA apart rather than 3.7 \AA. This behavior is not surprising since
	    GAFF models atoms as point charges and does not appropriately model the aromatic
	    $\pi-\pi$ interactions which would cause the monomers to stack closer together.
	    \item R-spots is missing in both places, at least visually. The tails in our model
	    are more disordered than the experimental system at 300K.  
	    \item R-helix does not appear in either case.
  \end{itemize}

@@

  \begin{figure}[!htb]
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:offset_integration}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:layered_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:layered_integration}
		\end{subfigure}
	\end{subfigure} 
    \caption{We hypothesize that R-spots is the result of ordered tail packing.
	  Defining the membrane plane to be 0\degree, we measured the angles between each
	  alkane chain tail centroid and its nearest neighbor centroids for the
	  equilibrated parallel displaced (a) and sandwiched (c) configurations. Peaks
	  that appear in each distribution are centered near $\pm~33\degree$. We radially
	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
	  configuration within the region bounding R-alkanes ((b) and (d) respectively).
	  Peaks appear in the same location as the angle distributions which corroborates
	  our hypothesis. Further, we note that the peaks are strongest in both plots
	  associated with the sandwiched configuration. As shown in Figure
	  \ref{fig:rz_layered}, systems simulated in the sandwiched configuration exhibit
	  more intense R-spots reflections. Note that plots of integrated intensity are
	  normalized so the average alkane intensity (excluding reflections $\pm
	  30\degree$ from the $q_z$ axis) is set to 1.  Plots are cut off for intensities
	  greater than 2 so peaks are more visible.}~\label{fig:tail_packing}
  \end{figure}

@@

  We can also produce R-helix if layers are not uniformly spaced. Rather, monomers might form 
  pairs that stack less than 3.7 \AA apart, and whose center of masses are spaced 7.4 \AA 
  from the next pair of monomers.(Figure reference)
  \begin{itemize}
  		\item To our knowledge, there have been no studies that specifically address the 
  		possibility of a configuration like this. 
  		\item Our forcefield causes our system to tend towards uniformly spaced layers. 
  		\item As expected, simulations of this type of system are only stable if position
  		restraints are applied to heavy atoms of the phenyl rings.
  		\item Many \textit{ab initio} studies have measured the equilibrium distance between
  		dimers of benzene and substituted benzene.
  		\item Tauer and Sherrill explored the binding energies of tetramers of benzene, but
  		did not explore the report the equilibrium distance between benzene rings. 
  		\item Even if there have been other studies of the equilibrium distance between 
  		stacks of benzene rings, it still does not model our system which has many 
  		electron-withdrawing groups and bulky substituents that would likely affect stacking
  		preferences. 
  \end{itemize}

  Our final hypothesized configuration which produces R-helix focus on the orientation of the
  tails. 
  \begin{itemize}
  		\item In this configuration, monomers are rotated so that the vector created by the  
  		bond extending from the carboxylate carbon to the phenyl ring is oriented $\pm 15 	
  		\degree$ with respect to the vector extending from the carboxylate carbon to the pore
  		center.
  		\item Every other monomer layer is rotated $+15 \degree$ and those in between are
  		rotated $-15 \degree$.
  		\item This configuration allows monomer tails to sit between adjacent monomer tails 
  		which may be the most favorable way for them to pack. 
  		\item This configuration is stable short-term while unrestrained.
  		\item This may be the most reasonable explanation for the appearance of R-helix. The
  		long-term stability of a configuration similar to this may be feasible if monomers
  		stay stacked 3.7 \AA apart. 
  \end{itemize}

>>>>

  %BJC3: Feel free to suggest different words
  \subsection{Density of monomers around pores}
  %MRS4: Perhaps instead of talking about ``layers'', we can talk about axial density correlations.  You can say that for the simulated systems, they appear to stay in highly ordered layers, but that the density correlations are low enough that layering is likely not a clear enough description.  
  Our simulations best support a model built with 5 monomers per layer based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 monomers per layer. 
  \begin{itemize}  
  %MRS4: somewhere you need to talk about the range of systems that were built, as that indicates the range of behaviors that are observed.
  		\item We built systems in both the parallel displaced and sandwiched configurations 			with layers initially spaced 3.7 \AA~apart according to the dry equilibration 
  		procedure.
  		\item The pore-to-pore spacing is stable in all systems are stable after 400 ns of 
  		simulation. Figure~\ref{fig:p2p} shows the equilibrated pore-to-pore distances for all 
  		systems tested. 
  		\item Systems built with 5 monomers in each layer equilibrate to a pore spacing that is 
  		most consistent with the experimental value of 4.12 nm derived from SAXS measurements 
	    (Figure~\ref{fig:SAXS}).
  \end{itemize}

@@

  The simulated XRD patterns produced from both systems show moderate qualitative 
  agreement with experiment. 
  \begin{itemize}
  		\item R-alkanes and R-pores appear in the expected location
    %MRS4: we will need to provide more details: more intense is just qualiatative.
  		\item R-pores is more intense than experiment, likely because we are simulating a 
		perfect, infinite hexagonal array. The real system has defects and domain misalignment
	    which decreases the overall intensity.
    %MRS4: comments from Matt suggest that domain misaligment shouldn't alone be responsible for the difference in intensity ratio. Some of the experiments should help explain it better. Let's talk!
	  \item R-$\pi$ appears at a lower $q_z$ value than experiment. In both systems, the
	    reflection reaches its maximum at c.a. $q_z=1.4$ which means that monomers prefer 
	    to stack c.a. 4.5 \AA apart rather than 3.7 \AA. This behavior is not surprising since
	    GAFF models atoms as point charges and does not appropriately model the aromatic
	    $\pi-\pi$ interactions which would cause the monomers to stack closer together.
	    \item R-spots is missing in both places, at least visually. The tails in our model
	    are more disordered than the experimental system at 300K.  
            %MRS4: are they really missing?  If Fig 7 is 300K, sandwiched seems to have it, and parallel displaced is hard to tell because it's covered by the main pi-pi-stacking
            %MRS4: interesting that the main pi-pi stacking follows the isotropc alkane curve so significantly.
	    \item R-helix does not appear in either case.
            %MRS4: is r-helix a good name, when a helix would appear on either side of the center, not the center itself?
  \end{itemize}

@@

  \begin{figure}[!htb]
  \centering
  	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
        		\centering
        		\includegraphics[width=\linewidth]{offset_tail_packing.png}
        		\caption{}~\label{fig:offset_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
		\centering
	        	\includegraphics[width=\linewidth]{offset_angle_v_I.png}
		        \caption{}~\label{fig:offset_integration}
		\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
	\centering
		\begin{subfigure}{0.45\textwidth}
	        \centering
		        \includegraphics[width=\linewidth]{angles_traj_layered.png}
		        \caption{}~\label{fig:layered_tails}
		\end{subfigure}
		\begin{subfigure}{0.45\textwidth}
        	\centering
		        \includegraphics[width=\linewidth]{layered_angle_v_I.png}
		        \caption{}~\label{fig:layered_integration}
		\end{subfigure}
	\end{subfigure} 
    %MRS4: caption is probably too long.
    \caption{We hypothesize that R-spots is the result of ordered tail packing.
	  Defining the membrane plane to be 0\degree, we measured the angles between each
	  alkane chain tail centroid and its nearest neighbor centroids for the
	  equilibrated parallel displaced (a) and sandwiched (c) configurations. Peaks
	  that appear in each distribution are centered near $\pm~33\degree$. We radially
	  integrated the simulated XRD patterns of the parallel displaced and sandwiched
	  configuration within the region bounding R-alkanes ((b) and (d) respectively).
	  Peaks appear in the same location as the angle distributions which corroborates
	  our hypothesis. Further, we note that the peaks are strongest in both plots
	  associated with the sandwiched configuration. As shown in Figure
	  \ref{fig:rz_layered}, systems simulated in the sandwiched configuration exhibit
	  more intense R-spots reflections. Note that plots of integrated intensity are
	  normalized so the average alkane intensity (excluding reflections $\pm
	  30\degree$ from the $q_z$ axis) is set to 1.  Plots are cut off for intensities
	  greater than 2 so peaks are more visible.}~\label{fig:tail_packing}
  \end{figure}

@@

  We can also produce R-helix if layers are not uniformly spaced. Rather, monomers might form 
  pairs that stack less than 3.7 \AA apart, and whose center of masses are spaced 7.4 \AA 
  from the next pair of monomers.(Figure reference)
  \begin{itemize}
  		\item To our knowledge, there have been no studies that specifically address the 
  		possibility of a configuration like this. 
  		\item Our forcefield causes our system to tend towards uniformly spaced layers. 
  		\item As expected, simulations of this type of system are only stable if position
  		restraints are applied to heavy atoms of the phenyl rings.
  		\item Many \textit{ab initio} studies have measured the equilibrium distance between
  		dimers of benzene and substituted benzene.
%MRS: don't need to include this point.
  		\item Tauer and Sherrill explored the binding energies of tetramers of benzene, but
  		did not explore the report the equilibrium distance between benzene rings. 
  		\item Even if there have been other studies of the equilibrium distance between 
  		stacks of benzene rings, it still does not model our system which has many 
  		electron-withdrawing groups and bulky substituents that would likely affect stacking
  		preferences. 
  \end{itemize}

  Our final hypothesized configuration which produces R-helix focus on the orientation of the
   tails. 
  %MRS4: we will need to wait to see the results for this come out to really discuss this well.
   \begin{itemize}
  		\item In this configuration, monomers are rotated so that the vector created by the  
  		bond extending from the carboxylate carbon to the phenyl ring is oriented $\pm 15 	
  		\degree$ with respect to the vector extending from the carboxylate carbon to the pore
  		center.
  		\item Every other monomer layer is rotated $+15 \degree$ and those in between are
  		rotated $-15 \degree$.
  		\item This configuration allows monomer tails to sit between adjacent monomer tails 
  		which may be the most favorable way for them to pack. 
  		\item This configuration is stable short-term while unrestrained.
  		\item This may be the most reasonable explanation for the appearance of R-helix. The
  		long-term stability of a configuration similar to this may be feasible if monomers
  		stay stacked 3.7 \AA apart. 
  \end{itemize}
